Assessing the impacts of time to detection distribution assumptions on detection probability estimation

### 2017-04-21 Draft.tex
Revisions of Reviewers' Comments.  Small changes to Draft.

Computation times for this simulation study were much greater than for the other studies because partitions of the cdf, e.g. $\Fm(C_i|\alpha,\varphi_s)$, had to be calculated separately for every survey; also, sampling often required 2-8 as many iterations.
Average times for exponential, lognormal, Weibull, and gamma model fits were 2.6, 5.1, 5.3, and 25+ hours, respectively, as compared to only 2, 3, 3.25, and 5.35 minutes for the intercept-only models.
Due to the computation times involved, we fit each model only once.

>>>>

Computation times for this simulation study were much greater than for the other studies because partitions of the cdf, e.g. $\Fm(C_i|\alpha,\varphi_s)$, had to be calculated separately for every survey; also, sampling often required 2-8 as many iterations.
Average times for exponential, lognormal, Weibull, and gamma model fits were 2.6, 5.1, 5.3, and 25+ hours, respectively, as compared to only 2.0, 3.0, 3.3, and 5.3 minutes for the intercept-only models.
Due to the computation times involved, we fit each model only once.

### 2017-04-21 ReviewerComments.tex
Revisions of Reviewers' Comments.  Small changes to Draft.

\newcommand{\pdet}{p^{(det)}}
\newcommand{\ind}{\stackrel{ind}{\sim}}
\newcommand{\Fm}{F_T^{(M)}}

\begin{document}
\itshape
Associate Editor:

@@

I have included several items for the authors to consider below and provide this review as an Ecologist and potential model user.
Several pieces of information are lacking from the manuscript that will be relevant to users of this method.
\begin{enumerate}
\item What types of data are relevant to each examined distribution (e.g., gamma, Weibull)?
\item What sample sizes (i.e., number of detections) are needed to obtain reliable estimates with CIs that are not so wide as to be meaningless?
\item What are approximate computation times for models of different complexity (e.g., days? weeks?).
\end{enumerate}
\begin{quote}
We address each of these in turn as they appear in the comments below.
\end{quote}

@@

Line 40-41.  Also worth mentioning caveats - e.g., greater imprecision and computation times.
\begin{quote}
\adam{I certainly don't intend to address either of these in the Abstract.  Both are discussed in the text.  Computation times are not addressed in the Discussion.  Let me know if you think otherwise.}
\end{quote}

Introduction\\
Line 36-41: I find mention of survival analyses here and later in the manuscript confusing for most readers - especially Ecologists, presuming this is the intended audience.  It may be due to the unorthodox use of time-to-detection instead of traditional time-to-event analyses often used to estimate survival.  I suggest either omitting the reference to survival analysis here and elsewhere in the manuscript, or using the time-to-event terminology in this sentence and providing citations for the cdf and pdfs outlined here for reference.  Then explain that within the manuscript you will subsequently refer to it as TTDD.  
\begin{quote}
We have made the equivalence more explicit: ``We analyze times to first detection as time-to-event data, as is done in parametric survival analysis, ..."
\end{quote}

3.1 \\
Line 60: In the context of estimating abundance of wildlife, justifying the inclusion of the Weibull and lognormal distributions because they are often used in survival analysis is weak.  Are there biologically plausible scenarios in which these distributions are appropriate given this type of data?  Justify here similar to the Gamma distribution.  Otherwise, omit.
\begin{quote}
We have added the following sentences to \ref{M-sec:exact_time}: ``Like the gamma TTDD, Weibull and lognormal TTDDs offer the flexibility of a two-parameter form and allow rates to increase or decrease during the survey.
All three TTDDs may provide reasonable empirical approximations of non-constant detection, though the shapes of the distributions differ, potentially leading to differing inference.
For instance, when detection rates vary across individuals, the result is a marginal detection rate that decreases over time.
Whether the marginal rate is best approximated by a gamma, lognormal, or Weibull TTDD depends on just how rates vary across individuals."

We appreciate the importance of providing biological justification for statistical assumptions.
It is always a good foundation.
That being said, the use of any time-to-detection distribution is a statistical approximation to empirical patterns.
If the dynamics of the system are more complicated than we can directly model, the best we can do is find a TTDD that reasonably describes the observed pattern.
For instance, if the arrival of the observer causes non-constant detection, we know neither how long that observer effects lasts nor how the degree of that effect changes over time.
Gamma, lognormal, and Weibull TTDDs all provide different models for that detection pattern with different inferences for tail probability.
\end{quote}

Simulation Analyses\\
Line 57-59: This is the first mention of peaked and non-peaked TTDDs.  Please define these terms and how they are manifested during point-count surveys in the Introduction - including a biological justification that warrants their inclusion in simulation studies.
\begin{quote}
We have given the definitions of peaked/nonpeaked their own paragraph in the Simulation Studies methodology (Section \ref{M-sec:sim}):
``In the following analyses we distinguish two categories of purely continuous TTDDs: peaked and nonpeaked.  
Detection rates $h(t)$ of peaked distributions generally increase over time, while detection rates of nonpeaked distributions generally decrease over time.
More formally, we define a peaked TTDD as having a mode greater than zero (or $C_1$ for lognormal) while a non-peaked TTDD has a mode of zero (or less than $C_1$), but we consider exponential TTDDs to be neither peaked nor nonpeaked."

@@

\item Simulations incorporating variable sample sizes to evaluate relative bias and precision would be very useful in terms of study design and applicability.  
\begin{quote}
We have extended our simulation study to include a variety of detection probabilities rather than a variety of sample sizes.
Both affect estimation and are worthy of investigation, but since the performance of unknown-$N$ binomial models generally deteriorates as values of $\pdet$ decrease, we chose to direct our attentions there.
Sections \ref{M-sec:mixture} and \ref{M-sec:family} have been reworked to detail the updated findings.
\end{quote}

\item How might study design impact bias and precision?  For example, length of survey relative to peaked TTDDs and pooling of time periods during data collection?  These are also scenarios that would benefit readers.  Alternatively, these issues could be addressed in the Discussion.
\begin{quote}
These are important decision in the design of surveys, but they are beyond the scope we have defined for this study.
Not having explicitly investigated them, we prefer not to speculate.
%\citet{Petit1995, Johnson2008, LeeMarsden2008} and \citet{Reidy2011} all address the effects of duration.
We have separated out a paragraph in the Discussion posing some design-related questions.
\end{quote}

@@

``Computation times for this simulation study were much greater than for the other studies because partitions of the cdf, e.g. $\Fm(C_i|\alpha,\varphi_s)$, had to be calculated separately for every survey; also, sampling often required 2-8 as many iterations.
Average times for exponential, lognormal, Weibull, and gamma model fits were 2.6, 5.1, 5.3, and 25+ hours, respectively, as compared to only 2, 3, 3.25, and 5.35 minutes for the intercept-only models.
Due to the computation times involved, we fit each model only once."
\end{quote}

\item I don’t fully appreciate the need for both 50\% and 90\% coverage estimates.  It seems one estimate would be sufficient, and typically 90\% or 95\% credible intervals are used with these types of analyses?
\begin{quote}
We agree that using both is redundant.
We now choose to report only 90\% credible intervals.
\end{quote}
\end{enumerate}

Results\\
Page 18, Figure 2:  Holy moly, the CIs of the mixture distributions are exceedingly wide given a sample size of 381 detections (which is a lot relative to many studies).
\begin{quote}
Clarification: We have 947 detections at 381 sites (which is \textit{really} a lot of detections).
We now clearly state in Section \ref{M-sec:data}: ``This dataset includes 947 Ovenbirds counted in 381 surveys at 65 sites with site-specific variables including site age,  stock density, and an indicator of select-/partial-cut logging during the 1990s."
\end{quote}

@@

Discussion\\
Page 21, Lines 12-16:  I do not agree with this assessment.  I think these models are appropriate for a particular subset of data - single species discrete-count surveys with a large sample size and relatively low availability (i.e., whether the animal provides a cue to an observer during the survey)   
\begin{quote}
We hope that clarifications above about abundance estimates and uncertainty resolve some of the reviewer's hesitations.
We have added single-species' to the draft.

\adam{Perhaps more explanation is required here.}
\end{quote}
where non-constant detection through time is suspected based on the behavioral ecology of the species.
\begin{quote}
This last clause implies that a constant-rate model should be the default.
We disagree.
Based on our results and applying the precautionary principle, we believe the burden of proof should rest with the analyst who wishes to assume constant detection.
This is a central point in our manuscript: the constant-rate assumption should not be the default.
\end{quote}

As the authors’ suggest, most point-count studies are designed to maximize availability, which is typically high for birds (e.g., 80-95\%) with perceptibility (e.g., the probability an observer detects a cue that is given by an animal) being the much larger source of bias.  Therefore, this model, without including a supplemental method to estimate perceptibility, is of limited use to many readers.
\begin{quote}
We agree.
This manuscript applies to removal-only analyses.
Still, the concept can be carried over to removal-distance analyses, as we describe in a paragraph of the Discussion.
The implementation will be more complicated and will vary depending on how removal- and distance-sampling are integrated.
\end{quote}
Further, although the method may be more accurate even for constant detection data, the loss in precision is such that users will likely not opt to use it unless they suspect non-constant detection through time.  Further, given its presumably arduous computation times (albeit unknown), adding a perceptibility component to the model would likely greatly increase computational demands with unknown implications to bias and precision.  Including a paragraph in the Discussion that outlines when the model would be most beneficial to users (e.g., what type of data, surveys, or sample sizes) and explicitly stating drawbacks (e.g., computation time, loss of precision) would greatly improve this section.  
\begin{quote}
\adam{I do not deem this necessary.  We have not explicitly studied sample size.  The rest is addressed at various locations in the manuscript but does not, I think, require a dedication paragraph in the Discussion.}
\end{quote}

@@

Diagnostics: Coverage. The idea of testing coverage is fantastic, but poorly implemented. First, the number of simulations (16 in Table 1) is exceedingly low to be able to reliably diagnose the patterns in coverage or the statistical explanation of these patterns. 
\begin{quote}
We answer this comments in two parts.
First, we agree that the number of simulations was inadequate for diagnosing model accuracy.
We have therefore increased to 100 the number of simulations in Sections \ref{M-sec:mixture} and \ref{M-sec:family}.
This has been made possible by improvements to Stan \citep{Rstan2016} and by streamlining our code for homogeneous surveys.
See the second paragraph of Section \ref{M-sec:simfull} for a summary of run times for the models currently.

Second, although the original number of simulations was inadequate for characterizing model accuracy, it nonetheless highlighted scenarios of gross inaccuracy, such as: (i) omitting a mixture component in modeling a peaked mixture dataset, or (ii) assuming constant detection when the rate varies during the survey period.
\end{quote}

Second, the statistical properties of the estimator of p(det) are likely depending on the size of the true value of p(det). Therefore, I think Table 1 should have been repeated for a whole range of values of the true value of p(det).
(Is a boundary like the one in Olkin et al 1981, for your case, a hard one such that below it estimation is bad, and above it estimation is ``uniformly" good?).
Without variation in ``true" simulated scenarios, it is easy to inadvertendly ``stack the deck" in favor or against a particular combination of settings (Particularly since your ``true" value of p is high: 0.8). A wide range of simulated truths is also necessary because to be useful, these methods should be widely applicable in the
tropics (low N's, low p's very often) as well as in temperate forests (large N's, large p's), for example.
\begin{quote}
We have repeated the simulations in Sections \ref{M-sec:mixture} and \ref{M-sec:family} at true detection probabilities $\pdet = 0.50, 0.65, 0.80$, and 0.95.
The findings have significantly added to our results and conclusions.

With reference to Olkin's finding that point estimates of $N_s$ are unstable unless $\pdet>0.41$, it is not a hard boundary.  
It varies by context, but the boundary is a general property of estimating $N$ in binomial unknown-$N$, unknown-$p$ problems.
Olkin's calculation derives from the relative sample mean and sample variance of repeated large samples with the same values of $N$ and $\pdet$.
As such, it is a best-case scenario.
Similar thresholds continue to recur in various abundance-estimating contexts, as demonstrated in these recent articles: 
\begin{itemize}
\item \citet{Veech2016}: advise caution when $p<0.5$ in the context of individual-level detection effects (no time-to-detection data). 
\item \citet{Field2016}: plots indicate uncertainty in $\hat{N}$ increase rapidly as $\pdet$ decreases below 0.40.  Methods include removal, double-observer, distance, and multiple-visit.
\item \citet{Davis2016}: report accurate $\hat{N}$ at $\pdet >0.40$ in a traditional removal-sampling context, though for small abundance ($N<50$) they required $\pdet > 0.7$.
\end{itemize}
\end{quote}

@@

We agree that discussions of identifiability and the flatness of the likelihood is very relevant, and we have introduced an explicity discussion of them in the Discussion.

As an informational note, the \texttt{R} package by Solymos was constructed for BUGS and JAGS, though it would not be difficult to adapt data cloning for Stan.
\end{quote}

@@

The authors could have crafted a beautiful and very telling graph (Figure 1) representing the multinomial intervals, the TTDD, the right censoring due to the end of the observation period, and the increased detection probability mixture component. Such figure (which is what I did by hand as I was reading the manuscript) would be a very useful guide in the reading of the paper.
\begin{quote}
We have added this as Figure \ref{M-fig:schematic}.
\end{quote}

>>>>

\newcommand{\pdet}{p^{(det)}}
\newcommand{\ind}{\stackrel{ind}{\sim}}
\newcommand{\dt}{\text{det}}
\newcommand{\ftdt}{f_{T|\dt}(t|\dt)}
\newcommand{\Fm}{F_T^{(M)}}

\begin{document}

\begin{quote}
We thank the reviewers for their comments.
We believe the manuscript is clearly a better document in consequence.
In particular, the reviewers encouraged us to generate more simulations --- in terms of both the number of replicates and the variety in true detection probabilities.
In pursuing these recommendations, we improved our simulation code to be more efficient by orders of magnitude for the covariate-free simulations.
Our results now more fully describe model performance across a range of true detection probabilities, and the patterns observed are more compelling on account of the greater number of replicates.
\end{quote}

\itshape
Associate Editor:

@@

I have included several items for the authors to consider below and provide this review as an Ecologist and potential model user.
Several pieces of information are lacking from the manuscript that will be relevant to users of this method.
\begin{enumerate}
\item What types of data are relevant to each examined distribution (e.g., gamma, Weibull)?

\begin{quote}\label{ans:one}
Thank you for raising this point.
Unlike the exponential and gamma TTDDs, the lognormal and Weibull do not have an immediate biological mechanism for interpreting hazard rates.
To address this issue, we have added to Section \ref{M-sec:exact_time}: ``Like the gamma TTDD, Weibull and lognormal TTDDs offer the flexibility of a two-parameter form and allow rates to increase or decrease during the survey.
All three TTDDs may provide reasonable empirical approximations of non-constant detection, though the shapes of the distributions differ, potentially leading to differing inference.
For instance, when detection rates vary across individuals, the result is a marginal detection rate that decreases over time.
Whether the marginal rate is best approximated by a gamma, lognormal, or Weibull TTDD depends on just how rates vary across individuals."

We definitely appreciate the importance of providing biological justification for statistical assumptions.
It is always a good foundation.
That being said, the use of any time-to-detection distribution is a statistical approximation to empirical patterns.
If the dynamics of the system are more complicated than we can directly model, the best we can do is find a TTDD that reasonably describes the observed pattern.
For instance, if the arrival of the observer causes non-constant detection, we know neither how long that observer effects lasts nor how the degree of that effect changes over time.
Gamma, lognormal, and Weibull TTDDs all provide different models for that detection pattern with different inferences for detection probability.

If an analyst does have a clear detection rate mechanism in mind, they can always fit our model using the appropriate hazard function and the relationship between it and its corresponding TTDD: $h(t) = f_T(t) / [1-F_T(t)]$.
\end{quote}

\item What sample sizes (i.e., number of detections) are needed to obtain reliable estimates with CIs that are not so wide as to be meaningless?

\begin{quote}
We fear the original version of Figure \ref{M-ovenposteriors} was confusing and led the reviewer to believe that CIs were larger than they in fact are.
It showed posterior credible intervals for \textit{uncounted} abundance, rather than the more intuitive \textit{total} abundance.
We have fixed the figure.
We hope the reviewer will agree that CIs are not always so wide as to be meaningless.

One reviewer recommended we simulate across multiple sample sizes; another reviewer recommended that we simulate across a variety of true detection probabilities.
Both are useful suggestions.
However, we decided to prioritize the simulation across detection probabilities, since papers on N-mixture models more often emphasize this side of model performance.
\end{quote}

\item What are approximate computation times for models of different complexity (e.g., days? weeks?).
\begin{quote}
Thanks to the encouragement from the reviewers to run more simulations, we revisited our code and improved efficiency by orders of magnitude for fitting interval-only models.
So, the first two simulation studies now use 100 replicates rather than then original 16.
We cannot realize such savings for models with heterogeneous detection across surveys.
We now cite runtime statistics in Section \ref{M-sec:simfull}: ``Average times for exponential, lognormal, Weibull, and gamma [heterogeneous] model fits were 2.6, 5.1, 5.3, and 25+ hours, respectively, as compared to only 2, 3, 3.25, and 5.35 minutes for the intercept-only models.''
\end{quote}

\end{enumerate}

@@

Line 40-41.  Also worth mentioning caveats - e.g., greater imprecision and computation times.
\begin{quote}

As noted above, we think imprecision appeared more exaggerated in our first submission than it in fact was, and we have improved computation times.
We address both issues in the text but feel that neither quite belongs in the Abstract.

We address computation times in Section \ref{M-sec:simfull}.
We address imprecision multiple places in the simulation results, Ovenbird results, and Discussion.
\end{quote}

Introduction\\
Line 36-41: I find mention of survival analyses here and later in the manuscript confusing for most readers - especially Ecologists, presuming this is the intended audience.  It may be due to the unorthodox use of time-to-detection instead of traditional time-to-event analyses often used to estimate survival.  I suggest either omitting the reference to survival analysis here and elsewhere in the manuscript, or using the time-to-event terminology in this sentence and providing citations for the cdf and pdfs outlined here for reference.  Then explain that within the manuscript you will subsequently refer to it as TTDD.  
\begin{quote}
We have made the equivalence more explicit: ``We analyze times to first detection as time-to-event data, as is done in parametric survival analysis, ..."
\jarad{We probably need to add more, e.g. intended audience. Philip?} 
\end{quote}

3.1 \\
Line 60: In the context of estimating abundance of wildlife, justifying the inclusion of the Weibull and lognormal distributions because they are often used in survival analysis is weak.  Are there biologically plausible scenarios in which these distributions are appropriate given this type of data?  Justify here similar to the Gamma distribution.  Otherwise, omit.
\begin{quote}
See the answer to Item 1 on Page~\pageref{ans:one} above for our full response.
\end{quote}

Simulation Analyses\\
Line 57-59: This is the first mention of peaked and non-peaked TTDDs.  Please define these terms and how they are manifested during point-count surveys in the Introduction - including a biological justification that warrants their inclusion in simulation studies.
\begin{quote}
We have separated the definitions of peaked/nonpeaked into own paragraph in the Simulation Studies methodology (Section \ref{M-sec:sim}):
``In the following analyses we distinguish two categories of purely continuous TTDDs: peaked and nonpeaked.  
Detection rates $h(t)$ of peaked distributions generally increase over time, while detection rates of nonpeaked distributions generally decrease over time.
More formally, we define a peaked TTDD as having a mode greater than zero (or $C_1$ for lognormal) while a non-peaked TTDD has a mode of zero (or less than $C_1$), but we consider exponential TTDDs to be neither peaked nor nonpeaked."

@@

\item Simulations incorporating variable sample sizes to evaluate relative bias and precision would be very useful in terms of study design and applicability.  
\begin{quote}
We thank the reviewers for pushing us to expand our simulation studies.
It led us to improvements in our simulation code, more compelling results (through increased replication), and characterization of model performance across more scenarios.
One reviewer asked us to simulated across a variety of detection probabilities, while the other asked us to simulation across sample sizes.
Both affect estimation and are worthy of investigation, but since the performance of unknown-$N$ binomial models generally deteriorates as values of $\pdet$ decrease, we chose to direct our attentions there.
Sections \ref{M-sec:mixture} and \ref{M-sec:family} have been reworked to detail the updated findings.
\end{quote}

\item How might study design impact bias and precision?  For example, length of survey relative to peaked TTDDs and pooling of time periods during data collection?  These are also scenarios that would benefit readers.  Alternatively, these issues could be addressed in the Discussion.
\begin{quote}
These are important decision in the design of surveys, but they are beyond the scope we have defined for this study.
Not having explicitly investigated them, we prefer not to speculate.
%\citet{Petit1995, Johnson2008, LeeMarsden2008} and \citet{Reidy2011} all address the effects of duration.
We have separated out a paragraph in the Discussion posing some design-related issues: (i) longer surveys, (ii) introduction of settling down periods, and (iii) collection of complete detection histories (not just first detections).
\end{quote}

@@

``Computation times for this simulation study were much greater than for the other studies because partitions of the cdf, e.g. $\Fm(C_i|\alpha,\varphi_s)$, had to be calculated separately for every survey; also, sampling often required 2-8 as many iterations.
Average times for exponential, lognormal, Weibull, and gamma model fits were 2.6, 5.1, 5.3, and 25+ hours, respectively, as compared to only 2.0, 3.0, 3.3, and 5.3 minutes for the intercept-only models.
Due to the computation times involved, we fit each model only once."
\end{quote}

\item I don’t fully appreciate the need for both 50\% and 90\% coverage estimates.  It seems one estimate would be sufficient, and typically 90\% or 95\% credible intervals are used with these types of analyses?
\begin{quote}
We agree that using both is redundant.
We now choose to report only 90\% credible intervals.
We still report 50\% intervals in the supplement.
\end{quote}
\end{enumerate}

Results\\
Page 18, Figure 2:  Holy moly, the CIs of the mixture distributions are exceedingly wide given a sample size of 381 detections (which is a lot relative to many studies).
\begin{quote}
Clarification: We actually have 947 detections at 381 sites (which is \textit{really} a lot).
We now clearly state in Section \ref{M-sec:data}: ``This dataset includes 947 Ovenbirds counted in 381 surveys at 65 sites with site-specific variables including site age,  stock density, and an indicator of select-/partial-cut logging during the 1990s."
We address CI widths in the next response.
\end{quote}

@@

Discussion\\
Page 21, Lines 12-16:  I do not agree with this assessment.  I think these models are appropriate for a particular subset of data - single species discrete-count surveys with a large sample size and relatively low availability (i.e., whether the animal provides a cue to an observer during the survey)   
\begin{quote}
We hope that clarifications above about abundance estimates and uncertainty resolve some of the reviewer's hesitations.
We have added `single-species' to the manuscript.
\end{quote}

where non-constant detection through time is suspected based on the behavioral ecology of the species.

\begin{quote}
This last clause implies that a constant-rate model should be the default.
We disagree.
Based on our results and applying the precautionary principle, we believe the burden of proof should rest with the analyst who wishes to assume constant detection.
This is a central point in our manuscript: the constant-rate assumption should not be the default.
\end{quote}

As the authors’ suggest, most point-count studies are designed to maximize availability, which is typically high for birds (e.g., 80-95\%) with perceptibility (e.g., the probability an observer detects a cue that is given by an animal) being the much larger source of bias.  Therefore, this model, without including a supplemental method to estimate perceptibility, is of limited use to many readers.
\begin{quote}
We agree.
This manuscript applies to removal-only analyses.
Still, the concept can be carried over to removal-distance analyses, as we describe in a paragraph of the Discussion.
The implementation will be more complicated and will vary depending on how removal- and distance-sampling are integrated.
This is ongoing work for us.
\end{quote}
Further, although the method may be more accurate even for constant detection data, the loss in precision is such that users will likely not opt to use it unless they suspect non-constant detection through time.  Further, given its presumably arduous computation times (albeit unknown), adding a perceptibility component to the model would likely greatly increase computational demands with unknown implications to bias and precision.  Including a paragraph in the Discussion that outlines when the model would be most beneficial to users (e.g., what type of data, surveys, or sample sizes) and explicitly stating drawbacks (e.g., computation time, loss of precision) would greatly improve this section.  
\begin{quote}
\adam{I do not deem this necessary.  We have not explicitly studied sample size.  The rest is addressed at various locations in the manuscript but does not, I think, require a dedication paragraph in the Discussion.}
\jarad{I'll have to re-read, but overall providing a summary for the reader
seems like a good idea.}
\end{quote}

@@

Diagnostics: Coverage. The idea of testing coverage is fantastic, but poorly implemented. First, the number of simulations (16 in Table 1) is exceedingly low to be able to reliably diagnose the patterns in coverage or the statistical explanation of these patterns. 
\begin{quote}
We agree that the number of simulations was inadequate for diagnosing model accuracy.
We have increased to 100 the number of simulations in Sections \ref{M-sec:mixture} and \ref{M-sec:family}.
This has been made possible by improvements to Stan \citep{Rstan2016} and by streamlining our code for homogeneous surveys.
\end{quote}

Second, the statistical properties of the estimator of p(det) are likely depending on the size of the true value of p(det). Therefore, I think Table 1 should have been repeated for a whole range of values of the true value of p(det).
(Is a boundary like the one in Olkin et al 1981, for your case, a hard one such that below it estimation is bad, and above it estimation is ``uniformly" good?).
Without variation in ``true" simulated scenarios, it is easy to inadvertendly ``stack the deck" in favor or against a particular combination of settings (Particularly since your ``true" value of p is high: 0.8). A wide range of simulated truths is also necessary because to be useful, these methods should be widely applicable in the
tropics (low N's, low p's very often) as well as in temperate forests (large N's, large p's), for example.
\begin{quote}
We have repeated the simulations in Sections \ref{M-sec:mixture} and \ref{M-sec:family} at true detection probabilities $\pdet = 0.50, 0.65, 0.80$, and 0.95.
The findings have significantly added to our results and conclusions.
The extra simulations demonstrate that, for nonpeaked datasets, the model returns similar detection estimates whether the true value of $\pdet$ is 0.50 or 0.65 or even somewhat 0.80.
For exponential and peaked datasets, the model is more able to return unbiased estimates.
Other major findings of our original manuscript -- the inadequacy of non-mixture or constant-rate models in many cases -- remain true across wide ranges of true values for $\pdet$.

%With reference to Olkin's finding that point estimates of $N_s$ are unstable unless $\pdet>0.41$, it is not a hard boundary.  
%It varies by context, but the boundary is a general property of estimating $N$ in binomial unknown-$N$, unknown-$p$ problems.
%Olkin's calculation derives from the relative sample mean and sample variance of repeated large samples with the same values of $N$ and $\pdet$.
%As such, it is a best-case scenario.
%Similar thresholds continue to recur in various abundance-estimating contexts, as demonstrated in these recent articles: 
%\begin{itemize}
%\item \citet{Veech2016}: advise caution when $p<0.5$ in the context of individual-level detection effects (no time-to-detection data). 
%\item \citet{Field2016}: plots indicate uncertainty in $\hat{N}$ increase rapidly as $\pdet$ decreases below 0.40.  Methods include removal, double-observer, distance, and multiple-visit.
%\item \citet{Davis2016}: report accurate $\hat{N}$ at $\pdet >0.40$ in a traditional removal-sampling context, though for small abundance ($N<50$) they required $\pdet > 0.7$.
%\end{itemize}
\end{quote}

@@

We agree that discussions of identifiability and the flatness of the likelihood is very relevant, and we have introduced an explicit discussion of them in the Discussion:

``Reduced model performance in the presence of low detection probabilities is common among abundance models.
We recommend the discussion in \citet{CoullAgresti1999}, elaborating key points here.
The essential problem is a flat log-likelihood.
For single-pass surveys, we cannot rely on repeated counts to improve our estimates.
Instead, the strategy of removal sampling is to use the observed pattern of detection times to estimate the proportion of individuals that would be detected if only the observation period lasted longer.  
As such, it is entirely reliant upon extrapolation based on an accurate fit of $\ftdt$.
When true detection probabilities are low, $\ftdt$ for nonpeaked data becomes flat.
Such a flat observed pattern provides little information and is well approximated by a wide variety of TTDDs, which vary greatly in their tail probabilities.
An assumption of constant detection limits the shape of $\ftdt$ and thereby constrains uncertainty but at the cost of potentially sizable bias.''
\end{quote}

@@

The authors could have crafted a beautiful and very telling graph (Figure 1) representing the multinomial intervals, the TTDD, the right censoring due to the end of the observation period, and the increased detection probability mixture component. Such figure (which is what I did by hand as I was reading the manuscript) would be a very useful guide in the reading of the paper.
\begin{quote}
Thank you for the suggestion.
We have added this as Figure \ref{M-fig:schematic}.
We agree that the figure is quite effective and should be a useful guide to readers of the paper.
\end{quote}
